$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-01 paper/paper.tex

Data type definitions use double lines and index-free synonyms as rule names (for ease of reference).
We otherwise use the constructor name as the name of a typing rule.
Universe levels and universe polymorphism are omitted for brevity --- all our types are of type $et$.
Implicit arguments are mentioned by type definitions but omitted in constructors.
$\type{TYPES}$ are in blue and uppercased (with indices as subscripts), $\constr{constructors}$ are in olive, $\field{fields}$ in red, and variables and functions in black.
Some constructor names are overloaded --- they and disambiguated by context.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Syntax}
\label{syntax}
We let $x, y,\ldots$ range over \emph{channel names} or \emph{variables} and
$P, Q,\ldots$ over processes.
The syntax of the \picalc{} \cite{Sangio01} is given by the following grammar.
\todo{maybe put both syntaxes in two columns to save space}
\begin{equation*}
  \begin{split}
    P,Q ::=      & \; \PO       &\text{(terminated process)}  \\
                |& \; (\new{}x)  P   & \text{(restriction)} \\
                |& \; \comp{P}{Q}  & \text{(parallel composition)} \\
                |& \; \recvp{x}{y}.P  & \text{(input)} \\
                |& \; \sendp{x}{y}.P   &\text{(output)}
  \end{split}
\end{equation*}
Process $\PO$ denotes the terminated process, where no operations can further occur.
Process $(\new{}x)P$ is the restriction process where channel $x$ is created new and is bound with scope $P$.
Process $\comp{P}{Q}$ is the parallel composition of processes $P$ and $Q$.
Processes $\recvp{x}{y}.P$ and $\sendp{x}{y}.P$ denote respectively the input and output processes of a variable/channel $y$ over a channel $x$, with continuation $P$.

@@

\todo{remove space between inferrules}
\begin{figure}[h]
\begin{mathpar}
  \datatype
  { }
  {P \eqeq Q : et}
  \; \textsc{StructCong}

>>>>

Data type definitions use double lines and index-free synonyms as rule names (for ease of reference).
We otherwise use the constructor name as the name of a typing rule.
Universe levels and universe polymorphism are omitted for brevity --- all our types are of type $\Set$.
Implicit arguments are mentioned by type definitions but omitted in constructors.
$\type{TYPES}$ are in blue and uppercased (with indices as subscripts), $\constr{constructors}$ are in olive, $\field{fields}$ in red, and variables and functions in black.
Some constructor names are overloaded --- they and disambiguated by context.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Syntax}
\label{syntax}
We let $x, y,\ldots$ range over \emph{channel names} or \emph{variables} and
$P, Q,\ldots$ over processes.
The syntax of the \picalc{} \cite{Sangio01} is given by the following grammar.
\todo{maybe put both syntaxes in two columns to save space}
\begin{equation*}
  \begin{split}
    P,Q ::=      & \; \PO       &\text{(terminated process)}  \\
                |& \; (\new{}x)  P   & \text{(restriction)} \\
                |& \; \comp{P}{Q}  & \text{(parallel composition)} \\
                |& \; \recvp{x}{y}. \; P  & \text{(input)} \\
                |& \; \sendp{x}{y}. \; P   &\text{(output)}
  \end{split}
\end{equation*}
Process $\PO$ denotes the terminated process, where no operations can further occur.
Process $(\new{}x)P$ is the restriction process where channel $x$ is created new and is bound with scope $P$.
Process $\comp{P}{Q}$ is the parallel composition of processes $P$ and $Q$.
Processes $\recvp{x}{y}.P$ and $\sendp{x}{y}.P$ denote respectively the input and output processes of a variable/channel $y$ over a channel $x$, with continuation $P$.

@@

\todo{remove space between inferrules}
\begin{figure}[h]
\begin{mathpar}
  \datatype
  { }
  {P \eqeq Q : \Set}
  \; \textsc{StructCong}
